NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-04-19 ms_nihao_budget.tex
add gas fraction in different phases figure and remove table 1

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations.
  A comparison of how the baryons distribute in the halo with 
  different masses. 
  The lines are color coded by their halo mass, which show a clear
  trend that the more massive halo preserve more baryons alone
  the radius.}
\label{fig:rps}
\end{figure}

@@

We tried to capture the behaviour of the baryonic mass fraction as a 
function of the halo mass using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line. These are 
measured in four different mass ranges, and are  summarized in Table.~\ref{tab:sigma}.

\begin{table}
\caption{Scatters for best fit parameters for the total baryonic mass 
fraction computed inside one virial radius, $R_{200}$,  as a function of halo mass $M_{200}$
in different mass ranges.} 
\begin{center}
\begin{tabular}{lc}
\hline
Mass Range & $\sigma $ \\
\hline
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$ & 0.151 \\
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$ & 0.236 \\
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$ & 0.125 \\
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$ & 0.0518 \\
\hline
\end{tabular}
\label{tab:sigma}
\end{center}
\end{table}

@@

@@

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=budget.eps,width=0.5\textwidth}
}
\caption{Baryonic budget (the fraction of different components) 
  of $3.5\times 10^{11} < M_{200}/\Msun <
  3.5 \times 10^{12}$ NIHAO galaxies (blue points 
  with 1$\sigma$ error bars) compared with observations of 
  M$_{200}$ = 10$^{12.2}$ $\Msun$ galaxies (shaded regions)
  }
\label{fig:comparison}
\end{figure}

%% TABLE 2
\begin{table*}
\caption{The baryonic budget parameters for galaxies in NIHAO sample
  in different mass bins. We refer to gas in the temperature range  T
  $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
  $10^7$ K as hot.}
\begin{center}
\begin{tabular}{ccccc}
\hline
\input{budgettable4.txt}
\hline
\end{tabular}
\label{tab:comperison}
\end{center}
\end{table*}

>>>>

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budgetpro.eps,width=0.99\textwidth}
}
\caption{Radial profile of the mass fraction of the gas in each phase
         to total baryon mass in each radial bin 
         at z=0 for all galaxies in NIHAO sample.
         Each solid line is from one galaxy and color coded with
         the halo mass.}
\label{fig:corona}
\end{figure*}

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations.
  A comparison of how the baryons distribute in the halo with 
  different masses. 
  The lines are color coded by their halo mass, which show a clear
  trend that the more massive halo preserve more baryons alone
  the radius.}
\label{fig:rps}
\end{figure}

@@

We tried to capture the behaviour of the baryonic mass fraction as a 
function of the halo mass using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
{\bf which are 0.151 for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.}

@@

\subsection{Mass budget of the corona}
\label{sec:corona}

In Fig.~\ref{fig:corona}, we present the radial distribution of 
gas in different phases normalized to the

@@

%% FIGURE 4
\begin{figure}
\centerline{
  \psfig{figure=budget.eps,width=0.5\textwidth}
}
\caption{Baryonic budget (the fraction of different components) 
  of $3.5\times 10^{11} < M_{200}/\Msun <
  3.5 \times 10^{12}$ NIHAO galaxies (blue points 
  with 1$\sigma$ error bars) compared with observations of 
  M$_{200}$ = 10$^{12.2}$ $\Msun$ galaxies (shaded regions)
  }
\label{fig:comparison}
\end{figure}

%% TABLE 1
\begin{table*}
\caption{The baryonic budget parameters for galaxies in NIHAO sample
  in different mass bins. We refer to gas in the temperature range  T
  $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
  $10^7$ K as hot.}
\begin{center}
\begin{tabular}{ccccc}
\hline
\input{budgettable4.txt}
\hline
\end{tabular}
\label{tab:comperison}
\end{center}
\end{table*}
